Seminar: Programming models and Code Generation\\ Winter Term 2014/2015\\ {\bf Quasi deterministic parallel programming using LVars}

### 2015-01-05 draft.tex
new

It adopts the basic approach of the par monad. The existing $par$ monad\cite{simon} in Haskell offers an API for parallel programming. It provides by default a work-stealing scheduler and supports forking tasks. The programmer specifies how information flows across computations but not the order in which they will be evaluated at runtime. Information flow is described using IVars. With

@@

If the Lvish code uses freeze then it is marked as QuasiDet or Det if it is fully deterministic. $runparIO$ allows us to execute Lvish code in the IO monad if the determinism level is arbitrary. $runparthenFreeze$s automatically freezes the Lvar when it returns back its exact value guaranteeing determinism.\\ \\

@@

Internally par monad represents computations in continuation passing style, in terms of their interpretation in the IO monad. The status bit of an LVar is tied together with a bag of waiting listeners, which include blocked gets and handlers.

>>>>

It adopts the basic approach of the $par$ monad. The existing $par$ monad\cite{simon} in Haskell offers an API for parallel programming. It provides by default a work-stealing scheduler and supports forking tasks. The programmer specifies how information flows across computations but not the order in which they will be evaluated at runtime. Information flow is described using IVars. With

@@

If the Lvish code uses $freeze$ then it is marked as \emph{QuasiDet} or \emph{Det} if it is fully deterministic. $runparIO$ allows us to execute Lvish code in the IO monad if the determinism level is arbitrary. $runparthenFreeze$ automatically freezes the Lvar when it returns back its exact value guaranteeing determinism.\\ \\

@@

Internally $par$ monad represents computations in continuation passing style, in terms of their interpretation in the IO monad. The status bit of an LVar is tied together with a bag of waiting listeners, which include blocked gets and handlers.
